Clinical Trial Data Analysis

### 2017-09-13 results/results.Rmd
Edits to text in clinical results, add correlation test, up the number of replications to 1e4

@@

The primary endpoint is `daily_hrdq`, a measure derived from other variables that were measured in the survey.
We show summary statistics for this outcome for each treatment group below.
```{r hrdq, results = "asis"}
daily_hrdq <- reshape_data("daily_hrdq")
summary_stats_hrdq <- cbind(summary(daily_hrdq$difference[daily_hrdq$tr == "B"]),
                            summary(daily_hrdq$difference[daily_hrdq$tr == "A"]))
colnames(summary_stats_hrdq) <- c("B", "A")
print(xtable(summary_stats_hrdq,
             caption = "Summary statistics for change in primary 
                        endpoint (daily hrdq) for the two treatment groups."),
      include.rownames = TRUE)
```

# Analysis - Primary endpoint
To illustrate the different methods, let's first restrict attention to the primary endpoint, `daily_hrdq`.
Throughout this section, we compare two models which both control for site ID.
The first model uses the outcome in week two as the dependent variable, controlling for the baseline score in the models with covariates.
The second model uses the difference between outcome and baseline score as its dependent variable.
The difference in the two models is how we control for the baseline measure.

@@

## Parametric ANCOVA
First, we do a standard parametric ANCOVA using the two models.
Under model 1, using the outcome as response and adjusting for the baseline value, treatment has a significant effect.
Under model 2, the significance goes away.
(Note that treatment is still coded as A and B with the character type. 
The `lm` function is smart enough to know that it should be coded as a factor, where we compare the effect of B relative to A,
and coerces the variable type from string to factor behind the scenes. 
Be very careful when you're doing this!
It is generally safer to change types yourself.)
```{r hrdq_parametric, results = "asis"}
# method 0: parametric ANCOVA
lm1 <- lm(Outcome ~ Baseline + tr + factor(SITEID), data = daily_hrdq)
print(xtable(summary(aov(lm1))), include.rownames = TRUE)
daily_hrdq$lm1_resid <- residuals(lm1)

@@

@@

Figure \ref{fig:hrdq_unadjusted_permutation} shows the permutation distributions of the simple difference in means for the two models.
Figure \ref{fig:hrdq_unadj_perm_withinstrata} shows the permutation distribution of the absolute value of the difference of means within strata, summed across strata.
These empirical permutation distributions are computed by randomly permuting treatment assignments within each site $10^4$ times and computing the statistic for each permutation.
The vertical line shows the observed value of the test statistic.
The $p$-value is two times the area of the permutation distribution to the right of the observed value;
it is the probability of observing a value at least as extreme (falling that far away from the center of the distribution) as the observed value.
There are several points to notice:

@@

@@

@@

For this dataset, we are guaranteed that treatment $Z$ is independent of $\varepsilon$, as it is randomized within site.
We check these associations using residual plots in Figure \ref{fig:residual_plots}.
Indeed, the distribution of residuals looks nearly equal between treatment groups in both models.
The distribution of residuals varies a bit across sites, but they all appear roughly centered around 0.
Sites 4 and 5 have larger variance in the differenced model.
This should not be an issue since we permute treatments within sites, independently across sites.
(In general, when treatment is not randomly assigned, this condition is necessary for the permutation test to be valid.)

```{r residual_plots, echo = FALSE, message = FALSE, fig.align = "center", fig.height = 5, fig.cap = "Residual plots of the linear regression of daily hrdq on treatment and covariates. These are done to check that treatment and covariates are uncorrelated with the regression errors for the Freedman and Lane style permutation test."}
p11 <- daily_hrdq %>% 
  select(-Baseline, -Outcome, -difference) %>% 
  melt(id.vars = c("SUBJID", "tr", "SITEID")) %>%
  filter(variable == "lm1_resid") %>% 
  ggplot(aes(x = factor(tr), y = value)) +
  geom_boxplot() + 
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Treatment") + ylab("Residual") + 
  ggtitle("Raw Outcome Model") +
  theme_bw()
p21 <- daily_hrdq %>% 
  select(-Baseline, -Outcome, -difference) %>%  
  melt(id.vars = c("SUBJID", "tr", "SITEID")) %>%
  filter(variable == "lm1_resid") %>% 
  ggplot(aes(x = factor(SITEID), y = value)) +
  geom_boxplot() +  
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Site ID") + ylab("Residual") + 
  ggtitle("Raw Outcome Model") +
  theme_bw()
p12 <- daily_hrdq %>% 
  select(-Baseline, -Outcome, -difference) %>% 
  melt(id.vars = c("SUBJID", "tr", "SITEID")) %>%
  filter(variable == "lm2_resid") %>% 
  ggplot(aes(x = factor(tr), y = value)) +
  geom_boxplot() +  
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Treatment") + ylab("Residual") +
  ggtitle("Differenced Model") +
  theme_bw()
p22 <- daily_hrdq %>% 
  select(-Baseline, -Outcome, -difference) %>%  
  melt(id.vars = c("SUBJID", "tr", "SITEID")) %>%
  filter(variable == "lm2_resid") %>% 
  ggplot(aes(x = factor(SITEID), y = value)) +
  geom_boxplot() +  
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Site ID") + ylab("Residual") +
  ggtitle("Differenced Model") +
  theme_bw()
grid.arrange(p12, p11, p22, p21, nrow = 2, ncol = 2)
```

@@

data.frame("perm" = c(lm1_t_distr, lm2_t_distr),
           "model" = c(rep("Outcome", length(lm1_t_distr)), 
                       rep("Differenced", length(lm2_t_distr))),
           "xintercept" = c(rep(observed_t1, length(lm1_t_distr)),
                            rep(observed_t2, length(lm2_t_distr)))) %>%
  ggplot(aes(x = perm, fill = model)) +
  geom_histogram() +
  facet_grid(~model) +
  geom_vline(aes(xintercept = xintercept)) +
  theme_bw() +
  labs(x = "t Statistic", y = "Frequency") +
  theme(legend.position = "none")

Table 2 shows the $p$-values for each of the four methods and the two models.
For the models using the raw outcome measure as the dependent variable, the effect of `daily_hrdq` is significant at the $0.05$ level in two of the five tests
and is significant at the $0.1$ level in four of the five tests.
It is never significant in the models using the difference from baseline to outcome.
As expected, the stratified permutation test using the sum of differences in means across sites has low power.

```{r primary_endpoint_res, results = "asis", fig.align = "center", fig.cap = "Comparison of $p$-values for two measures (average outcome during treatment vs. difference of average outcome and average baseline) of the primary endpoint."}

outcome_pvalues <- c(summary(aov(lm1))[[1]]["trB", "Pr(>F)"],
                     diff_means_pvalue1,
                     diff_means_bystrata_pvalue1,
                     lm_pvalue_1,
                     fl_pvalue_1)
differenced_pvalues <- c(summary(aov(lm2))[[1]]["trB", "Pr(>F)"],
                     diff_means_pvalue2,
                     diff_means_bystrata_pvalue2,
                     lm_pvalue_2,
                     fl_pvalue_2)
pvalues_table <- cbind(differenced_pvalues, outcome_pvalues)

@@

# Analysis - Secondary endpoints

We restrict our attention to the model using treatment measurement and controlling for the baseline, as this is what RB's original analysis does.
We run this procedure for all seven continuous endpoints.
Table 3 shows the results.

@@

tests <- c("ANCOVA", "Stratified perm", "LM perm", "Residual perm")
pvalues_table_contin <- as.data.frame(matrix(NA, nrow = length(continuous_vars), ncol = 4))
i <- 0

for(col in continuous_vars){
  i <- i+1
  tmpdata <- reshape_data(col)
  lm1 <- lm(Outcome ~ Baseline + tr + factor(SITEID), data = tmpdata)
  pvalues_table_contin[i, 1] <- summary(aov(lm1))[[1]]["tr", "Pr(>F)"]

  observed_diff_means <- mean(tmpdata[tmpdata$tr == "B", ]$Outcome) - mean(tmpdata[tmpdata$tr == "A", ]$Outcome)
  diff_means_distr <- stratified_two_sample(group = tmpdata$tr, response = tmpdata$Outcome, stratum = tmpdata$SITEID, reps = 1e3)
  pvalues_table_contin[i, 2] <- t2p(observed_diff_means, diff_means_distr, alternative = "two-sided")

  observed_t <- summary(lm1)[["coefficients"]]["trB", "t value"]
  lm1_t_distr <-  replicate(1e3, {
    tmpdata$tr_perm <- permute_within_groups(tmpdata$tr, tmpdata$SITEID)
  lm1_perm <- lm(Outcome ~ Baseline + tr_perm + factor(SITEID), data = tmpdata)
  summary(lm1_perm)[["coefficients"]]["tr_permB", "t value"]
  })
  pvalues_table_contin[i, 3] <- t2p(observed_t, lm1_t_distr, alternative = "two-sided")

  lm_no_tr <- lm(Outcome ~ Baseline + factor(SITEID), data = tmpdata)
  lm_resid <- residuals(lm_no_tr)
  lm_yhat <- fitted(lm_no_tr)
  observed_t <- summary(lm1)[["coefficients"]]["trB", "t value"]
  lm_t_distr <-  replicate(1e3, {
      lm_resid_perm <- permute_within_groups(lm_resid, tmpdata$SITEID)
      tmpdata$response_fl <-  lm_yhat + lm_resid_perm
      lm_perm <- lm(response_fl ~ Baseline + tr + factor(SITEID), data = tmpdata)
      summary(lm_perm)[["coefficients"]]["trB", "t value"]
})

  pvalues_table_contin[i, 4] <- t2p(observed_t, lm_t_distr, alternative = "two-sided")
}
```
```{r results_table_print, results = "asis", fig.align = "center", fig.cap = "Comparison of $p$-values from four tests, for each continuous endpoint."}
rownames(pvalues_table_contin) <- continuous_vars
colnames(pvalues_table_contin) <- tests

>>>>

# Summary

We reanalyzed a dataset from a clinical trial comparing the effectiveness of two treatments for gastroesophageal reflux disease (GERD). 
Patients were treated at eight sites in two different countries. 
At each site, patients were randomly assigned one of two treatments. 
Patients were observed for a week before receiving treatment and for a week after receiving treatment. 
On each of the fourteen days of observation, patients responded to a survey about their heartburn, regurgitation, and dyspepsia frequency and severity. 
These endpoints were measured on a discrete scale. 
There were several additional endpoints, such as daily regurgitation, daily “hrdq”, and daily dyspepsia, calculated from the survey measures. 
Daily “hrdq” was the primary endpoint. 
To reduce day-to-day variation, we averaged the measures from each week to obtain two observations per patient, one pre-treatment and one post-treatment.

In what follows, we compare the parametric ANCOVA, the stratified permutation test, and the two linear model-based permutation tests.
We begin by walking through the tests in detail using the primary endpoint.
We illustrate different ways of controlling for the baseline measure: including it in the model and using change scores as the dependent variable.
The original analysis of the dataset controls for baseline by including it in the model, so for consistency we choose that method for our final analysis.
We conclude by running the tests for each endpoint.

@@

Table 1 shows the correlation between baseline and outcome for each variable.
Correlations range between 0.548 and 0.696.
This suggests that using the difference in outcome and baseline as the dependent variable in the following models might yield higher power than controlling for baseline as a covariate.

```{r corr_table_print, results = "asis", fig.align = "center", fig.cap = "Correlation between baseline and outcome, for each continuous endpoint."}

baseline_outcome_corr <- rep(0, length(continuous_vars))
for(i in seq_along(continuous_vars)){
  col <- continuous_vars[i]
  tmpdata <- reshape_data(col)
  baseline_outcome_corr[i] <- cor(tmpdata$Baseline, tmpdata$Outcome)
}

baseline_outcome_corr <- data.frame(baseline_outcome_corr)
colnames(baseline_outcome_corr) <- "Correlation"
rownames(baseline_outcome_corr) <- continuous_vars

summarytabc <- xtable(baseline_outcome_corr, 
             digits = 3,
             align = paste0(c("r|", rep("p{1in}", 1)), 
                            collapse = ""),
             caption = "Correlation between baseline and outcome, for each continuous endpoint.",
             label = "tab:clinical_corr")
print(summarytabc, include.rownames = TRUE)
```

# Analysis - Primary endpoint
To illustrate the different methods, let's first restrict attention to the primary endpoint, `daily_hrdq`.
Throughout this section, we compare two models which both control for site ID.
The first model uses the outcome in week two as the dependent variable, controlling for the baseline score in the models with covariates.
The second model uses the difference between outcome and baseline score as its dependent variable.
The difference in the two models is the way in which we control for the baseline measure.

@@

The primary endpoint is `daily_hrdq`, a measure derived from other variables that were measured in the survey.
We show summary statistics for the change from baseline for each treatment group below.
Based on these statistics, it appears that members of group B had both larger outcomes and larger changes from baseline than group A.
We will do two-sided hypothesis tests to assess whether the difference between groups A and B is meaningfully different from zero.
```{r hrdq, results = "asis"}
daily_hrdq <- reshape_data("daily_hrdq")
summary_stats_hrdq <- cbind(summary(daily_hrdq$Outcome[daily_hrdq$tr == "B"]),
                            summary(daily_hrdq$Outcome[daily_hrdq$tr == "A"]),
                            summary(daily_hrdq$difference[daily_hrdq$tr == "B"]),
                            summary(daily_hrdq$difference[daily_hrdq$tr == "A"]))
colnames(summary_stats_hrdq) <- c("B Outcome", "A Outcome", "B Difference", "A Difference")
print(xtable(summary_stats_hrdq,
             caption = "Summary statistics for change in primary 
                        endpoint (daily hrdq) for the two treatment groups."),
      include.rownames = TRUE)
```

## Parametric ANCOVA

```{r hrdq_parametric, results = "asis"}
# method 0: parametric ANCOVA
lm1 <- lm(Outcome ~ Baseline + tr + factor(SITEID), data = daily_hrdq)
print(xtable(summary(aov(lm1))), include.rownames = TRUE)
daily_hrdq$lm1_resid <- residuals(lm1)

@@

First, we do a standard parametric ANCOVA using the two models.
Under model 1, using the outcome as response and adjusting for the baseline value, treatment has a significant effect with p-value `r round(summary(aov(lm1))[[1]]["tr", "Pr(>F)"], 3)`.
Under model 2, the significance goes away (p-value of `r round(summary(aov(lm2))[[1]]["tr", "Pr(>F)"], 3)`).
(Note that treatment is still coded as A and B with the character type. 
The `lm` function is smart enough to know that it should be coded as a factor, where we compare the effect of B relative to A,
and coerces the variable type from string to factor behind the scenes. 
Be very careful when you're doing this!
It is generally safer to change types yourself.)

@@

@@

The empirical permutation distributions are computed by randomly permuting treatment assignments within each site $10^4$ times and computing the statistic for each permutation.
A vertical line indicates the observed value of the test statistic.
The $p$-value is two times the area of the permutation distribution to the right of the observed value;
it is the probability of observing a value at least as extreme (falling that far away from the center of the distribution) as the observed value.
Figure \ref{fig:hrdq_unadjusted_permutation} shows the permutation distributions of the simple difference in means for the two models.
The p-values for the differenced model and raw outcome model are `r round(diff_means_pvalue2, 3)` and `r round(diff_means_pvalue1, 3)`, respectively.
Figure \ref{fig:hrdq_unadj_perm_withinstrata} shows the permutation distribution of the absolute value of the difference of means within strata, summed across strata.
The p-values for the differenced model and raw outcome model are `r round(diff_means_bystrata_pvalue2, 3)` and `r round(diff_means_bystrata_pvalue1, 3)`, respectively.

There are several points to notice:

@@

The p-values for the differenced model and raw outcome model are `r round(lm_pvalue_2, 3)` and `r round(lm_pvalue_1, 3)`, respectively.

@@

For this dataset, we are guaranteed that treatment $Z$ is independent of $\varepsilon$, as it is randomized within site.
However, the randomization does not guarantee that $\varepsilon$ is independent baseline measure, conditional on site.
We check this associations using residual plots in Figure \ref{fig:residual_plots}.
The distribution of residuals varies a bit across sites, but they all appear roughly centered around 0.

```{r test_correlation_resid, results='asis'}
obs_corr <- daily_hrdq %>% group_by(SITEID) %>% summarise("n"=n(), "Correlation"=cor(lm1_resid, Baseline))
corr_pvalues <- rep(0, 8)

for(i in unique(daily_hrdq$SITEID)){
  tmp <- daily_hrdq %>% filter(SITEID == i)
  corr_distr <- replicate(1e4,{
    cor(permute(tmp$lm1_resid), tmp$Baseline)
  })
  corr_pvalues[i] <- t2p(unlist(obs_corr[i, "Correlation"]), corr_distr, alternative = "two-sided")
}

fisher_combined_corr <- pchisq(fisher(corr_pvalues), df = 2*length(corr_pvalues), lower.tail = FALSE)

obs_corr <- obs_corr %>% mutate("P-value" = corr_pvalues)
print(xtable(obs_corr, digits = 2,
             caption = "Permutation test $p$-values for the correlation between baseline daily hrdq and residuals."))
```

By construction of the linear model, the correlation between the baseline measure and the residuals is zero.
However, we would like to check formally that $\varepsilon$ is independent baseline measure for each site, using the residuals as a proxy for $\varepsilon$.
To do so, we conduct independent permutation tests within each stratum using the Pearson correlation as the statistic.
Table 3 shows the results of this test: while the correlation between baseline and residuals appears high, it is not statistically significant at the 5\% level in any stratum.
The Fisher's combined $p$-value for the 8 strata is `r round(fisher_combined_corr, 2)`, so there is no evidence that the independence assumption is violated.

```{r residual_plots, echo = FALSE, message = FALSE, fig.align = "center", fig.height = 5, fig.cap = "Residual plots of the linear regression of daily hrdq on treatment and covariates. These are done to check that treatment and covariates are uncorrelated with the regression errors for the Freedman and Lane style permutation test."}
p11 <- daily_hrdq %>% 
  select(-Outcome, -difference) %>% 
  melt(id.vars = c("SUBJID", "Baseline", "SITEID")) %>%
  filter(variable == "lm1_resid") %>% 
  ggplot(aes(x = Baseline, y = as.numeric(value))) +
  geom_point() + 
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Baseline") + ylab("Residual") + 
  ggtitle("Raw Outcome Model") +
  theme_bw()
p21 <- daily_hrdq %>% 
  select(-Baseline, -Outcome, -difference) %>%  
  melt(id.vars = c("SUBJID", "tr", "SITEID")) %>%
  filter(variable == "lm1_resid") %>% 
  ggplot(aes(x = factor(SITEID), y = as.numeric(value))) +
  geom_boxplot() +  
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Site ID") + ylab("Residual") + 
  ggtitle("Raw Outcome Model") +
  theme_bw()
p22 <- daily_hrdq %>% 
  select(-Baseline, -Outcome, -difference) %>%  
  melt(id.vars = c("SUBJID", "tr", "SITEID")) %>%
  filter(variable == "lm2_resid") %>% 
  ggplot(aes(x = factor(SITEID), y = as.numeric(value))) +
  geom_boxplot() +  
  ylim(-2.25, 2.25)+
  geom_hline(yintercept = 0, linetype = "dashed") +
  xlab("Site ID") + ylab("Residual") +
  ggtitle("Differenced Model") +
  theme_bw()
grid.arrange( p21, p11, p22, layout_matrix = rbind(c(1, 2), c(3, NA)))
```

@@

data.frame("perm" = c(lm1_t_distr, lm2_t_distr),
           "model" = c(rep("Raw Outcome Model", length(lm1_t_distr)), 
                       rep("Differenced Model", length(lm2_t_distr))),
           "xintercept" = c(rep(observed_t1, length(lm1_t_distr)),
                            rep(observed_t2, length(lm2_t_distr)))) %>%
  ggplot(aes(x = perm, fill = model)) +
  geom_histogram() +
  facet_grid(~model) +
  geom_vline(aes(xintercept = xintercept)) +
  theme_bw() +
  labs(x = "t Statistic", y = "Frequency") +
  theme(legend.position = "none")

```
The p-values for the differenced model and raw outcome model are `r round(fl_pvalue_2, 3)` and `r round(fl_pvalue_1, 3)`, respectively.

## Summary

Table 4 shows the $p$-values for each of the five methods and the two methods of controlling for the baseline.
For the models using the raw outcome measure as the dependent variable, the effect of `daily_hrdq` is significant at the $0.05$ level in two of the five tests
and is significant at the $0.1$ level in four of the five tests.
It is never significant in the models using the difference from baseline to outcome.
As expected, the stratified permutation test using the sum of differences in means across sites has low power.

```{r primary_endpoint_res, echo=FALSE, results = "asis", fig.align = "center", fig.cap = "Comparison of $p$-values for two measures (average outcome during treatment vs. difference of average outcome and average baseline) of the primary endpoint."}

outcome_pvalues <- c(summary(aov(lm1))[[1]]["tr", "Pr(>F)"],
                     diff_means_pvalue1,
                     diff_means_bystrata_pvalue1,
                     lm_pvalue_1,
                     fl_pvalue_1)
differenced_pvalues <- c(summary(aov(lm2))[[1]]["tr", "Pr(>F)"],
                     diff_means_pvalue2,
                     diff_means_bystrata_pvalue2,
                     lm_pvalue_2,
                     fl_pvalue_2)
pvalues_table <- cbind(differenced_pvalues, outcome_pvalues)

@@

\newpage
# Analysis - Secondary endpoints

We restrict our attention to the model using treatment measurement and controlling for the baseline, as this is what RB's original analysis does.
We run this procedure for all seven continuous endpoints.
Table 5 shows the results.

@@

tests <- c("ANCOVA", "Stratified perm", "LM perm", "Residual perm")
pvalues_table_contin <- as.data.frame(matrix(NA, nrow = length(continuous_vars), ncol = 4))
baseline_outcome_corr <- rep(0, length(continuous_vars))

for(i in seq_along(continuous_vars)){
  col <- continuous_vars[i]
  tmpdata <- reshape_data(col)
  baseline_outcome_corr[i] <- cor(tmpdata$Baseline, tmpdata$Outcome)

  lm1 <- lm(Outcome ~ Baseline + tr + factor(SITEID), data = tmpdata)
  pvalues_table_contin[i, 1] <- summary(aov(lm1))[[1]]["tr", "Pr(>F)"]

  observed_diff_means <- mean(tmpdata[tmpdata$tr == "B", ]$Outcome) - mean(tmpdata[tmpdata$tr == "A", ]$Outcome)
  diff_means_distr <- stratified_two_sample(group = tmpdata$tr, response = tmpdata$Outcome, stratum = tmpdata$SITEID, reps = 1e4)
  pvalues_table_contin[i, 2] <- t2p(observed_diff_means, diff_means_distr, alternative = "two-sided")

  observed_t <- summary(lm1)[["coefficients"]]["trB", "t value"]
  lm1_t_distr <-  replicate(1e4, {
    tmpdata$tr_perm <- permute_within_groups(tmpdata$tr, tmpdata$SITEID)
  lm1_perm <- lm(Outcome ~ Baseline + tr_perm + factor(SITEID), data = tmpdata)
  summary(lm1_perm)[["coefficients"]]["tr_permB", "t value"]
  })
  pvalues_table_contin[i, 3] <- t2p(observed_t, lm1_t_distr, alternative = "two-sided")

  lm_no_tr <- lm(Outcome ~ Baseline + factor(SITEID), data = tmpdata)
  lm_resid <- residuals(lm_no_tr)
  lm_yhat <- fitted(lm_no_tr)
  observed_t <- summary(lm1)[["coefficients"]]["trB", "t value"]
  lm_t_distr <-  replicate(1e4, {
      lm_resid_perm <- permute_within_groups(lm_resid, tmpdata$SITEID)
      tmpdata$response_fl <-  lm_yhat + lm_resid_perm
      lm_perm <- lm(response_fl ~ Baseline + tr + factor(SITEID), data = tmpdata)
      summary(lm_perm)[["coefficients"]]["trB", "t value"]
})

  pvalues_table_contin[i, 4] <- t2p(observed_t, lm_t_distr, alternative = "two-sided")
}
```

```{r results_table_print, echo=FALSE, results = "asis", fig.align = "center", fig.cap = "Comparison of $p$-values from four tests, for each continuous endpoint."}
rownames(pvalues_table_contin) <- continuous_vars
colnames(pvalues_table_contin) <- tests
